\primarysection{Experience}

\runsubsection{VMware}
\descript{| Software Engineer}
\location{Boston, MA (Remote) \\ August 2021 - Present}
\begin{tightemize}
    \item Worked on VMware Cloud Director, a cloud infrastructure platform.
    \item Cloud director manages provisioning cloud workloads and provides an
        interface for serving cloud resources to tenants.
    \item Improved catalog synchronization and implemented permission
        restrictions for certain types of users.
\end{tightemize}
\subsectionsep

\runsubsection{UMass Cryptography Lab}
\descript{| Undergraduate Researcher}
\location{Amherst, MA \\ January 2020 - May 2021}
\begin{tightemize}
    \item Worked with professor Adam O'Neill on a cryptanalysis of the Bitcoin
        Pseudorandom Number Generator.
    \item Formally modeled bitcoin's \texttt{random.cpp}
\end{tightemize}
\subsectionsep

\runsubsection{VMware}
\descript{| Software Engineer Intern, VMware Tanzu}
\location{Amherst, MA (Remote) \\ May 2020 - August 2020}
\begin{tightemize}
    \item Implemented internal support for the Cluster API Docker provider
        (CAPD) in Tanzu Kubernetes Grid (TKG) in Go.
\end{tightemize}
\subsectionsep

\runsubsection{MIT Digital Currency Initiative}
\descript{| Undergraduate Researcher}
\location{Cambridge, MA \\ January 2019 - September 2019}
\begin{tightemize}
  \item Designed algorithms to mitigate the front-running problem in
      cryptocurrency and securities exchanges, and increase overall
      public audit-ability of exchanges.
  \item Wrote an academic paper which introduces new cryptographic protocols to
      decrease trust needed in cryptocurrency and securities exchanges.
  \item Worked with layer 2 technologies such as the Bitcoin Lightning
      Network and hash time lock contracts (HTLCs) to implement
      non-custodial exchange technology.
  \item Implemented research while building OpenCX, an open source
      cryptocurrency exchange framework.
\end{tightemize}
\subsectionsep

% \runsubsection{Charles River Analytics}
% \descript{| Software Engineer Intern}
% \location{Cambridge, MA \\ June 2018 - August 2018}
% \begin{tightemize}
% \item Created framework to score causal analysis algorithms for time
%     series analysis in Python.
% \item Implemented various statistical analysis methods to detect
%     causality in time series data with Granger, Pearson, and
%     Convergent Cross Mapping tests.
% \item Demonstrated an increase in precision and recall for detecting
%     causal effects in sets of arbitrary time series data.
% \end{tightemize}
% \subsectionsep

% \runsubsection{Funkitron}
% \descript{| Software Engineer Intern}
% \location{Cambridge, MA \\ May 2017 - June 2017}
% \begin{tightemize}
% \item Created an online, player-versus-player version of Funkitron's Cascade,
%   a candy-crush-like matching game where players match certain tiles to try to
%   defeat their opponents.
% \item Implemented serialization and deserialization for game events and messages.
% \end{tightemize}
% \subsectionsep