\primarysection{projects}

\runsubsection{\href{https://github.com/mit-dci/opencx}{OpenCX}}
\descript{| Open-source project - Author}
\begin{tightemize}
  \item Author of OpenCX, the first open-source toolkit for building asset exchanges.
  \item Developed state of the art features for non-custodial trading, privacy-preserving proofs of solvency, verifiable delay functions, and complete public verifiability of exchange behavior.
  \item Designed and implemented a novel front-running resistant and non-custodial exchange protocol using tools from OpenCX.
\end{tightemize}
\subsectionsep

\runsubsection{\href{https://github.com/mit-dci/lit}{Lit}}
\descript{| Open-source project - Contributor}
\begin{tightemize}
  \item Contributor to lit, a Lightning Network node implementation compatible with multiple cryptocurrencies, including Bitcoin, Litecoin, and Vertcoin.
  \item Implemented event bus system and other improvements to the software in an effort to make it more interoperable with other software.
\end{tightemize}
\subsectionsep

\runsubsection{\href{https://github.com/bsathvik/binance-dex}{Binance DEX}}
\descript{| Open-source project - co-author}
\begin{tightemize}
  \item Modified the Bitcoin codebase to implement asset creation, limit GTC
    order creation, and delegate voting on the blockchain.
  \item Designed and implemented the \textbf{first ever} Delegated Proof of
    Stake consensus algorithm that works with the UTXO Model.
  \item Won \textbf{\$50,000} for DEX implementation. Technical report and
    design rationale can be read at
    \href{http://dancline.net/binance/}{dancline.net/binance}.
\end{tightemize}
% !!! IMPORTANT: NO SUBSECTIONSEP AT LAST ITEM